%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins

\name{Naeem Quddus} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{713~$\cdot$~775~$\cdot$~1383  \\  nquddus94@gmail.com} % Your phone number and email
\address{713\ 775\ 1383  \\  nquddus94@gmail.com} % Your phone number and email

\begin{document}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}


% Numbers to add:
    % Companion app downloaded 1.2 million times in the first year
    % Nearly a quarter million go's sold in the first quarter
    % GDPR fines can be up to 4% of a firm's annual worldwide revenue from previous fin year

% Words to include
    % Engineered - open ended enough to be for team or single person

  \begin{rSubsection}{Oculus VR - Meta}{May 2017 - June 2018}{Software Engineer - Oculus Mobile App Team}{Menlo Park, CA}
  \item Built and released the companion app for Oculus Go and Oculus
      Quest on iOS and Android.
      Worked full stack on mobile pairing user flow and Bluetooth pairing protocols.
      Designed and implemented new standards for the standalone VR first time user experience. 
      Developed and engineered Oculus mobile GDPR compliance process and strategy.
  \item Outcomes: 1.2 million app downloads in the first year, quarter million Oculus Go headsets sold in the first quarter, 
      Secured against potential GDPR compliance fines of 1.6 billion dollars 
  \end{rSubsection}

%------------------------------------------------

  \begin{rSubsection}{Oculus VR - Meta}{May 2016 - August 2016}{Software Engineering Intern - Developer Platform team}{Menlo Park, CA}
  \item Redesigned and implemented a new navigation system for the Oculus
      developer dashboard website. Worked with designers and content strategists
      to create a new user experience. Created a rich text editor to allow
      developers to write formatted descriptions. 
  \end{rSubsection}

%------------------------------------------------


  \begin{rSubsection}{Bloomberg LP}{May 2015 - August 2015}{Software Engineering Intern - Mortgage Development team}{New York City, NY}
  \item Designed and created new system to handle workflows for individuals.
      System designed to automatically generate, assign, and monitor progress of
      work items in real time. Helps streamline triage and work blockage
      analysis for project leads. Abstracted interface to allow for new projects
      and workflows to be added smoothly. 
%  \item Development tools: Python for programming majority of system scripts. C++ to interact with Bloomberg data systems. Tickets managed by JIRA, and project tracking software. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Indeed.com}{May 2014 - August 2014}{Software Engineering Intern - Aggregation team}{Austin, TX}
\item Programmed a service to query information from Twitter to find possible
    job application pages. Wrote and trained a naive Bayesian classifier to
    parse the html content of candidate pages and classify pages, filtering out
    98\% of undesired pages. 
%\item Development tools: Java for primary development of both systems. Guice and Ivy for dependency injection and management. RabbitMQ used for intersystem communications. 
\end{rSubsection}

\end{rSection}
%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

  \begin{rSubsection}{Radiosity Global Illuminator}{}{}{}
  \item Implementation of a rendering algorithm generating scenes with global
      illumination. Divides a given environment into discrete polygons which
      radiate light until color convergence. 
  \end{rSubsection}

  \begin{rSubsection}{Cloth Simulator}{}{}{}
  \item Implementation of \textit{Large Steps in Cloth Simulation} by Baraff and
      Witkin and \textit{Robust Treatment of Collisions, Contact and Friction
      for Cloth Animation} by Bridson et al. 
  \item Collisions prevented by inelastic impulses and spring based repulsion
      forces and detected by axis aligned bounding volume hierarchy.
  \end{rSubsection}

\end{rSection}
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education and Accomplishments}

  {\bf University of Texas, Austin} \hfill {\em May 2017} \\ 
  B.S. in Computer Science $\cdot$ Turing Scholars Honors Program  \\
  Overall GPA: 3.85

    \begin{rSubsection}{Competitive Programming}{}{}{}
        \item Member of UT's International Collegiate Programming Contest team at South Central Regional \hfill {\em October 2014}
        \item {\bf 1st Place} Google Games Austin \hfill {\em April 2015}
        \item {\bf 2nd Place} Microsoft Coding Challenge \hfill {\em September 2015}
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  Proficient & Java, Javascript, React Native \\
  Familiar & Python, C/C++, Bash \\ 
  Tools & Git, Travis CI, Vim, Guice, GraphQL/Relay, Redux
\end{tabular}

\end{rSection}

%
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
